### 2016-11-21 paper/intro.tex
minor changes

Several approaches have been proposed in the literature to address the
regression testing problem.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  It is important to note,
however, that balancing the test workload, either within or across
machines, is a popular, sound, and practical approach to address
testing cost and can't be neglected.  Furtheremore, this approach is
complementary to those proposed in the literature. For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.  As additional examples, Google's TAP
and Microsoft's CloudBuild distribute task workloads in the cloud.
Note, that the alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building a
server farm (for increased security) is a legitimate approach to
mitigate the regression testing problem at large organizations.
However, this solution may not be economically viable for smaller
projects.

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
%%  LocalWords:  Ekstazi github CloudBuild PWA groupon

>>>>

Several approaches have been proposed in the literature to address the
regression testing problem.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  It is important to note,
however, that balancing the test workload, either within or across
machines, is a popular, sound, and practical approach to address
testing cost and can't be neglected.  Furthermore, this approach is
complementary to those proposed in the literature. For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.  As additional examples, Google's TAP
and Microsoft's CloudBuild distribute task workloads in the cloud.
Note, that the alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} or even building a
server farm (for increased security) is a legitimate approach to
mitigate the regression testing problem at large organizations.
However, this solution may not be economically viable for smaller
projects with heavy testing loads.

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
%%  LocalWords:  Ekstazi github CloudBuild PWA groupon criticality
